<header style="text-align: center">

### 2019-05-19 report/report.Rmd
Add plot of diverted flights

```{r}
bru <- 'EBBR'
event <- c('2016-02-28', '2016-03-01')
```
```{r, fig.align='center'}
ddr.map(data$real$routes[1:1000], autocenter = FALSE)
```

@@

@@

>>>>

```{r, fig.align='center'}
ddr.map(data$real$routes[1:1000], autocenter = FALSE)
```

@@

On the day of the event, March 22, 2016, there were a total of `r div[, .N]` diverted flights that had intended to land on Brussels Airport (EBBR).

```{r, fig.align='center'}
ddr.map(data$real$routes[id %in% div[, id]], autocenter = FALSE)
```

## TODO

@@

The nearby airports to EBBR include:
- EBCI (Brussels South Charleroi)
- EBLF (Liège)
- EHEH (Eindhoven)
- EBAW (Antwerp)
- LFQQ (Lille)
